Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-16 paper.qmd
Updated Figure 16 color range for high-d error cluster

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist) |>
  filter(!(row_number() %in% c(155, 554, 140)))

@@

tsne_minst_scaled_temp <- tsne_minst_scaled |>
  mutate(cluster = if_else((tSNE1 <= 0.92) & (tSNE1 >= 0.76) & (tSNE2 <= 0.62) & (tSNE2 >= 0.44), "small_clust", "big_clust"))

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = tsne_minst_scaled_temp,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c("#999999",'#ff7f00')) +
  interior_annotation("a", sc_ltr_pos_mnist) +
  theme(aspect.ratio = 1,
        legend.position = "none")

>>>>

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist) #|>
  #filter(!(row_number() %in% c(155, 554, 140)))

@@

tsne_minst_scaled_temp <- tsne_minst_scaled |>
  mutate(cluster = if_else((tSNE1 <= 1) & (tSNE1 >= 0.78) & (tSNE2 <= 0.62) & (tSNE2 >= 0.39), "small_clust", "big_clust"))

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = tsne_minst_scaled_temp,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c("#999999",'#ff7f00')) +
  interior_annotation("a", sc_ltr_pos_mnist) +
  theme(legend.position = "none")
